%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Class
% Version 2.0 (12/10/23)
%
% This class originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Omar Roldan
% Based on a template by  Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
\usepackage{multicol}
\setlength{\columnsep}{0mm}
%----------------------------------------------------------------------------------------
\usepackage{lipsum}  


\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.5\textwidth} 
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	{ \fontsize{16}{20} \textcolor{black}{\textbf{\MakeUppercase{Mohammad Abu-Shelbaia}}}} % First name
	
	\vspace{6pt}
	
	{\Large \href{mailto:mabushelbaia@gmail.com}{mabushelbaia@gmail.com}} 
 
	\vspace{6pt}
	
{\Large (+970) 059-415-6035} 
\end{minipage}
\hfill
\begin{minipage}[t]{0.2\textwidth} % 20% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning mini pages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	
\end{minipage}
\begin{minipage}[t]{0.27\textwidth} % 27% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning mini pages
	
	\icon{Globe}{11}{\href{http://mabushelbaia.me}{mabushelbaia.me}}\\ 
    \icon{Github}{11}{\href{https://github.com/mabushelbaia}{github.com/mabushelbaia}}\\
    \icon{MapMarker}{11}{Ramallah, Palestine}\\
    
\end{minipage}


%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.46\textwidth}
    \cvsect{Summary}
	\vspace{-6pt}
    \textbf{Backend Developer}
    \begin{enumerate}[noitemsep]
        \item  Birzeit University Graduate with a Computer Engineering degree.
        \item  Expertise in full-stack web development using Django and Tailwind CSS\@.
        \item  Skilled in Python for automation, web scraping, and backend services.
    \end{enumerate}
   
    
   
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.465\textwidth}
    \cvsect{Skills}
    \vspace{-6pt}
    
    \begin{minipage}[t]{0.2\textwidth}
        \textbf{Languages:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.73\textwidth}
        Python, LaTeX, Markdown, Bash, Assembly, Java, C, SQL, HTML, CSS
    \end{minipage}
    \vspace{4mm}
    
    \begin{minipage}[t]{0.2\textwidth}
        \textbf{Technologies:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.73\textwidth}
        Git, FastAPI, Asyncio, Django, Tailwind CSS, Docker, PostgreSQL, Arduino, Nginx, Gunicorn
    \end{minipage}
    
    
\end{minipage}

% %----------------------------------------------------------------------------------------
% %	EXPERIENCE
% %----------------------------------------------------------------------------------------
\cvsect{Experience}
\begin{entrylist}
    \entry
        {3/2024 -- 7/2024}
        {Backend Developer Intern}
        {Silal}
        {\vspace{-10pt}
        \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
            \item Developed and maintained backend services using the Django framework.
            \item Utilized Docker for containerization and deployment, ensuring a consistent development and production environment.
            \item Integrated PostgreSQL as the primary database, optimizing queries and maintaining data integrity.
            \item Configured and managed Nginx as a reverse proxy server to handle client requests and serve static files efficiently.
            \item Deployed and managed WSGI applications using Gunicorn to handle Django web application processes.
            \item Utilized backend services with the user interface, utilizing Tailwind CSS for styling.
            \item Conducted code reviews and debugging to maintain high code quality and performance.
            \item Implemented authentication and authorization mechanisms to secure applications.
        \end{itemize} 
        \texttt{Docker} \slashsep \texttt{PostgreSQL} \slashsep \texttt{Nginx} \slashsep \texttt{Gunicorn} \slashsep \texttt{Django} \slashsep \texttt{Tailwind CSS}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	Projects
%----------------------------------------------------------------------------------------
\cvsect{Projects}
\begin{entrylist}
    \entry
		{Web Scrapping \\ Python, iCal}
		{Course Schedule}
		{\href{https://github.com/mabushelbaia/Course-Schedule}{\textcolor{blue}{github.com}}}
		{Developed a Python script to automate the extraction of weekly schedules from my university website and convert them into recurring iCal events. This project aimed to improve personal organization and time management by eliminating manual schedule data entry.}
    % \entry
    %     {Web Scrapping \\ Python, Threads}
    %     {NotesForProfessionals Scraper}
    %     {\href{https://github.com/mabushelbaia/NotesForProfessionals}{\textcolor{blue}{github.com}}}
    %     {Developed a Python script to scrape all the books/covers from the NotesForProfessionals website and download them to the local machine. Utilized threading to improve performance and synchronously download the assets.} 
    \entry
        {Django, Tailwind CSS \\ Nginx, Gunicorn}
        {Django Bookstore}
        {\href{https://github.com/mabushelbaia/django-bookstore}{\textcolor{blue}{github.com}}}
        {Developed a full-stack web application using Django and Tailwind CSS to display a collection of books. Utilized Nginx as a reverse proxy server and Gunicorn as the WSGI server to deploy the application using Docker`'. The project aimed to showcase skills in web development and backend services.}
    \entry
        {Robotics\\ ESP32, Arduino}
        {Micromouse Robot}
        {\href{https://github.com/mabushelbaia/Micromouse}{\textcolor{blue}{github.com}}}
        {Designed and implemented a maze-solving robot using the ESP32 microcontroller and the Arduino framework. The robot was programmed to autonomously navigate a maze and find the shortest path to the center using the Flood Fill algorithm.}
        
	\entry
		{Embedded Systems\\ PIC16f877A-Assembly}
		{PIC16f877A Calculator}
		{\href{https://github.com/mabushelbaia/PIC16F877A-Calculator}{\textcolor{blue}{github.com}}}
		{Developed a functional calculator on a PIC16f877A microcontroller, showcasing skills in embedded systems design and assembly language programming.}


\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Education}
\begin{entrylist}
    \entry
		{9/2020 - 7/2024}
		{Birzeit University}
		{Bachelor}
		{Computer Enginering\\
        \texttt{Cumulative Average: 87\%}
    }
    \entry
        {28th July 2024}
        {Udacity}
        {Nanodegree Certificate}
        {Data Analyst\\
        \href{https://www.udacity.com/certificate/e/3aa7c17a-0cbc-11ef-b565-af2bfee1c67d}{\texttt{Certificate Link}}
    }
\end{entrylist}





%----------------------------------------------------------------------------------------
%	LANGUAGES
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
	\cvsect{Languages}
    \vspace{-6pt}
    
    \hspace{26mm} \textbf{English} - \href{https://cert.efset.org/Lymieh}{C2 (CEFR)}, \textbf{ Arabic} - Native \\
    \hspace{26mm} 

\end{document}
