%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Class
% Version 2.0 (12/10/23)
%
% This class originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Omar Roldan
% Based on a template by  Jan Vorisek (jan@vorisek.com)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
\usepackage{multicol}
\setlength{\columnsep}{0mm}
%----------------------------------------------------------------------------------------
\usepackage{lipsum}  


\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.5\textwidth} 
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	{ \fontsize{16}{20} \textcolor{black}{\textbf{\MakeUppercase{Mohammad Abu-Shelbaia}}}} % First name
	
	\vspace{6pt}
	
	{\Large \href{mailto:mabushelbaia@gmail.com}{mabushelbaia@gmail.com}} 
 
	\vspace{6pt}
	
{\Large (+970) 059-415-6035} 
\end{minipage}
\hfill
\begin{minipage}[t]{0.2\textwidth} % 20% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning mini pages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	
\end{minipage}
\begin{minipage}[t]{0.27\textwidth} % 27% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning mini pages
	
	\icon{Globe}{11}{\href{http://mabushelbaia.github.io}{mabushelbaia.com}}\\ 
    \icon{Github}{11}{\href{https://github.com/mabushelbaia}{github.com/mabushelbaia}}\\
    \icon{MapMarker}{11}{Ramallah, Palestine}\\
    
\end{minipage}


%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.46\textwidth}
    \cvsect{Summary}
    Graduated with excellence from Birzeit University with a degree in Computer Engineering. Currently working as a Teaching and Research Assistant at the same institution. Experienced in full-stack web development. Proficient in Python, with a strong focus on automation, web scraping, and backend services.
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.465\textwidth}
    \cvsect{Skills}
    \vspace{-6pt}
    
    \begin{minipage}[t]{0.2\textwidth}
        \textbf{Languages:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.73\textwidth}
        Python, LaTeX, Markdown, Bash, Assembly, Java, C, SQL, HTML, CSS
    \end{minipage}
    \vspace{4mm}
    
    \begin{minipage}[t]{0.2\textwidth}
        \textbf{Technologies:}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.73\textwidth}
        Git, FastAPI, Flask, Asyncio, Django, Tailwind CSS, Docker, PostgreSQL, Arduino, Nginx, Gunicorn
    \end{minipage}
    
    
\end{minipage}

% %----------------------------------------------------------------------------------------
% %	EXPERIENCE
% %----------------------------------------------------------------------------------------
\cvsect{Experience}
\begin{entrylist}

    \entry
    {9/2024 -- Present}
    {Teaching And Research Assistant}
    {\href{https://www.birzeit.edu/en}{\textcolor{blue}{Birzeit University}}}
    {
        Assisted in delivering laboratory sessions on microcontroller programming and embedded systems. Provided mentorship and support to students, evaluated assignments, and contributed to the preparation of lab materials.
    }
    % {\vspace{-10pt}
    % \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
    %     \item Delivered laboratory sessions on Linux and microcontroller programming with tailored materials.
    %     \item Provided mentorship and technical guidance to students on assignments and projects.
    %     \item Developed practical exam scenarios and evaluated student performance.
    % \end{itemize}}    
    \entry
        {7/2024 -- 12/2024}
        {Backend Developer}
        {{\href{https://www.silal.app/en}{\textcolor{blue}{Silal}}}}
        { Contributed to the development and maintenance of a data processing pipeline for managing and analyzing product data. Wrote unit tests to ensure the reliability of Flask API endpoints.}
        % {\vspace{-10pt}
        % \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
        %     \item Continued developing and maintaining backend services using the Django framework.
        %     \item Built SEO-friendly product listing pipelines, integrating FastAPI with OpenAI's GPT for content generation.
        %     \item Deployed containerized services with Docker, maintaining efficient CI/CD pipelines.
        %     \item Enhanced system performance by optimizing database queries and backend logic.
        % \end{itemize} }
    
    \entry
        {3/2024 -- 7/2024}
        {Backend Developer Intern}
        {{\href{https://www.silal.app/en}{\textcolor{blue}{Silal}}}}
        {
            {Built a full-stack bookstore application using Django and Tailwind CSS, implementing core functionality and an intuitive user interface. Deployed the application with Docker Compose, using Nginx, Gunicorn, and PostgreSQL for a robust and production-ready setup.}  
        }
        % {\vspace{-10pt}
        % \begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt, leftmargin=-1pt]
        %     \item Assisted in building and maintaining backend services using Django and PostgreSQL.
        %     \item Utilized Docker for containerization, ensuring smooth development and deployment workflows.
        %     \item Contributed to application styling with Tailwind CSS and integrated backend services with the UI.
        % \end{itemize}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	Projects
%----------------------------------------------------------------------------------------
\cvsect{Projects}
\begin{entrylist}
    \entry
		{Web Scrapping \\ Python, iCal}
		{Course Schedule}
		{\href{https://github.com/mabushelbaia/Course-Schedule}{\textcolor{blue}{github.com}}}
		{Developed a Python script to automate the extraction of weekly schedules from my university website and convert them into recurring iCal events. This project aimed to improve personal organization and time management by eliminating manual schedule data entry.}
    % \entry
    %     {Web Scrapping \\ Python, Threads}
    %     {NotesForProfessionals Scraper}
    %     {\href{https://github.com/mabushelbaia/NotesForProfessionals}{\textcolor{blue}{github.com}}}
    %     {Developed a Python script to scrape all the books/covers from the NotesForProfessionals website and download them to the local machine. Utilized threading to improve performance and synchronously download the assets.} 
    \entry
        {Django, Tailwind CSS \\ Nginx, Gunicorn}
        {Django Bookstore}
        {\href{https://github.com/mabushelbaia/django-bookstore}{\textcolor{blue}{github.com}}}
        {Developed a full-stack web application using Django and Tailwind CSS to display a collection of books. Utilized Nginx as a reverse proxy server and Gunicorn as the WSGI server to deploy the application using Docker`'. The project aimed to showcase skills in web development and backend services.}
    \entry
        {Robotics\\ ESP32, Arduino}
        {Micromouse Robot}
        {\href{https://github.com/mabushelbaia/Micromouse}{\textcolor{blue}{github.com}}}
        {Designed and implemented a maze-solving robot using the ESP32 microcontroller and the Arduino framework. The robot was programmed to autonomously navigate a maze and find the shortest path to the center using the Flood Fill algorithm.}
        
	\entry
		{Embedded Systems\\ PIC16f877A-Assembly}
		{PIC16f877A Calculator}
		{\href{https://github.com/mabushelbaia/PIC16F877A-Calculator}{\textcolor{blue}{github.com}}}
		{Developed a functional calculator on a PIC16f877A microcontroller, showcasing skills in embedded systems design and assembly language programming.}


\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
\cvsect{Education}
\begin{entrylist}
    \entry
		{9/2020 - 7/2024}
		{Birzeit University}
		{Bachelor}
		{Computer Enginering\\
        \texttt{Cumulative Average: 87\%}
    }
    \entry
        {28th July 2024}
        {Udacity}
        {Nanodegree Certificate}
        {Data Analyst\\
        \href{https://www.udacity.com/certificate/e/3aa7c17a-0cbc-11ef-b565-af2bfee1c67d}{\texttt{Certificate Link}}
    }
\end{entrylist}





%----------------------------------------------------------------------------------------
%	LANGUAGES
%----------------------------------------------------------------------------------------
\vspace{-10 pt}
	\cvsect{Languages}
    \vspace{-6pt}
    
    \hspace{26mm} \textbf{English} - \href{https://cert.efset.org/Lymieh}{C2 (CEFR)}, \textbf{ Arabic} - Native \\
    \hspace{26mm} 

\end{document}
